---
title: "# Replication file for Figure 1 in Key and Sumner (2019)"
author: "Monica Perez"
date: "5/27/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 
```{r}
#setwd("D:/Dropbox/Gendered Research Agendas/")

#install.packages(c("here", "remotes"))
#remotes::install_github("benmarwick/wordcountaddin")

library(here)
here::here("data")

#sig <- read.csv("output-for-figure.csv")
sig <- read.csv(here("data", "output-for-figure.csv"))
```

```{r wordcount}
#wordcountaddin::word_count("source/Repl_plot-file.Rmd")
wordcountaddin::word_count((here("source", "Repl_plot-file.Rmd")))

```


```{r onlyFigure1, fig.width = 12, fig.height = 9}
#windows(width=12,height=12) # I think this only works on PCs.
#MP commented as it only works for PC, instead changed size in header of chunk or the graph displays incomplete in html.

# 1. Open jpeg file
#jpeg(here("output", "onlyPlotFigure1.jpg"))

#MP changed segments (background) color to blue for contrast
par(mar=c(3,16,2,1))
plot(sig$coefficient,c(1:length(sig$coefficient)),yaxt="n",pch=16,xlab="more likely among men                           more likely among women",ylab="",
     main="Gendered Topic Prevalences",xlim=c(-.02,.02),bty="n",xaxt="n",col=col,type="n")
segments(y0=c(1:61),x0=-.03,x1=.02,lty=3,col="blue")
points(sig$coefficient,c(1:length(sig$coefficient)),pch=16)
axis(1,at=c(-0.015,0,0.015),c("more prevalent among men","equal","more prevalent among women"))
segments(x0=sig$coefficient-1.96*sig$stderr,x1=sig$coefficient+1.96*sig$stderr,
         y0=c(1:length(sig$coefficient)))
segments(y0=0,y1=length(sig$coefficient),x0=0,lty=2)
axis(2,at=c(1:length(sig$coefficient)),sig$shorttopic,las=2,cex.axis=.8)

# end of file
```


Because I got a warning I looked at this:
> Output created: Repl_plot-file.html
> Warning message:
> In doTryCatch(return(expr), name, parentenv, handler) :
>  supplied color is neither numeric nor character

I found a really old post (R 2.4 2007) (https://stat.ethz.ch/pipermail/r-help/2007-August/137848.html)
that states this was a bug in lattice that should have been fixed. I loaded #lattice" but didn't close the warning.

"Note that the last component 'fill' is a factor (which is "not numeric
nor character", at least in a zen kind of way). I presume you are
somehow protecting 'col' from becoming a factor, and that does not
translate to 'fill'." 
